Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
a markup -> markup

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.  BDD
includes TDD, amongst other software development methodologies, but
with a terminology and mindset  shifted towards specification instead
of testing.  In BDD, specifications can be used for automatic testing.

@@

\begin{itemize}
\item Define a new Haddock markup for examples.
\item Define a new Haddock markup for properties.
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
\end{itemize}

@@

\noindent First, we introduce a new Haddock markup for the example.
In this paper, we use {\tt >>>} which is the same as Python's one.
Here is an example:

@@

\noindent To specify properties, we also propose a new markup. In this paper, we
use the {\tt prop>} prefix. We can write non-quantified properties as follows:

>>>>

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.  BDD
includes TDD, amongst other software development methods, but
with a terminology and mindset  shifted towards specification instead
of testing.  In BDD, specifications can be used for automatic testing.

@@

\begin{itemize}
\item Define new Haddock markup for examples.
\item Define new Haddock markup for properties.
\item Bring Doctest from the Python community to the Haskell
community and integrate it with QuickCheck.
\end{itemize}

@@

\noindent First, we introduce new Haddock markup for the example.
In this paper, we use {\tt >>>} which is the same as Python's one.
Here is an example:

@@

\noindent To specify properties, we also propose new markup. In this paper, we
use the {\tt prop>} prefix. We can write non-quantified properties as follows:
